\documentclass[a4paper,10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage[colorlinks=true,linkcolor=black,anchorcolor=black,citecolor=black,filecolor=black,menucolor=black,runcolor=black,urlcolor=black]{hyperref}

\newcommand{\dates}{\hfill\textit}

\titleformat{\section}
{\Large\bfseries}
{}
{0em}
{}[\titlerule \vspace{0.5em}]

\titleformat{\subsection}[runin]
{\large\bfseries}
{}
{0em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{}
{1em}
{}
[ : ]

\titleformat{\paragraph}
{}
{}
{0em}
{}

\titlespacing{\section}{0em}{1em}{0em}
\titlespacing{\subsection}{0em}{1em}{0em}
\titlespacing{\subsubsection}{0em}{0.4em}{1em}
\titlespacing{\paragraph}{0em}{0em}{0em}

\title{R\'esum\'e}
\author{Albert Matthew Alejo}
\pagenumbering{gobble}

\newcommand{\yourName}{Albert Matthew Alejo}
\newcommand{\yourWebsite}{https://mattalejo.com}
\newcommand{\yourEmail}{albert.alejo@obf.ateneo.edu}
\newcommand{\yourPhone}{+63 920 840 8888 }
\newcommand{\githubUserName}{mattalejo}
\newcommand{\linkedInUserName}{mattalejo}


\begin{document}

\begin{center}
\textbf{\huge \yourName} \\ \vspace{0.25em}
\small \yourPhone $|$ 
\href{mailto:\yourEmail}{\underline{\yourEmail}} $|$ 
\href{https://linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
\href{https://github.com/\githubUserName}{\underline{github/\githubUserName}}
\end{center}
\vspace{0.25em}

\section{Work Experience}

\subsection{Lumbricina}

\dates{2021 Apr - present}

\paragraph{Chief Financial Officer}

Handles the finances of the biotechnology startup

Reports financial- and fiscal-related matters to the CEO


\section{Education}

\subsection{Ateneo de Manila University}

\dates{2020 Sept - 2024 (expected graduation)}

\paragraph{Quezon City, Philippines}

BS/M Applied Mathematics with Specialization in Mathematical Finance

\subsection{PAREF Southridge} 

\dates{2014 Jun - 2020 May}

\paragraph{Muntinlupa City, Philippines}

High School - STEM Strand


\section{Skills}

\subsubsection{Languages}

English (fluent), Filipino (fluent)

\subsubsection{Finance/Accounting}

Uses Excel and Google Sheets for basic bookkeeping.

\subsubsection{Programming/Scripting languages}

R, Python

\subsubsection{Data modelling}

MATLAB

\subsubsection{Markup language}

\LaTeX, HTML, CSS, Markdown

\subsubsection{Image processing}

Adept at using Photoshop and Illustrator

\subsubsection{Video editing}

Uses Davinci Resolve for basic cutting and colour grading.

\subsubsection{Miscellaneous}

Can use Microsoft Office and Google Suite for basic productivity work. Adept at using either GNU/Linux or Windows.


\section{Affiliations}

\subsection{Studybuddy (Ateneo Gabay)}

\dates{2020 Nov - present}

\paragraph{Core Team, UI/UX Designer}

An initiative to create a university social network centered in academic fora. 

\subsection{New York Academy of Sciences}

\dates{2019 - 2020}

\paragraph{Young Member of the Academy}

Scientific society with over 1,700 young members worldwide.

Submitted an innovative solution for space exploration.

\subsection{Fathers' Day Registration Committee (PAREF Southridge)}

\dates{2018 Aug - 2020 Feb}

\paragraph{Committee Head}

Responsible with the entrance booth of the event and entrance ticket sales for guest

Accounts the scores of the rival houses of the school

\subsection{Mathematics Trainers' Guild}

\dates{2013 - 2018}

\paragraph{Participant}

Trains participants for international math contests

\section{Awards}

\subsection{Financial Aid Scholar}

\dates{2020 - present}

\paragraph{Ateneo de Manila University}

Given to financially challenged applicants with consistent academic performance and intellectual ability, and the the potential for greater service in the future.


\subsection{Merit Scholar}

\dates{2020 - present}

\paragraph{Department of Science and Technology - Science Education Institute}


Awarded to students with high aptitude in science and mathematics and are willing to pursue careers in the fields of science and technology

\subsection{Youth Excellence in Science Award}

\dates{2017}

\paragraph{DOST-SEI}

Award for exemplary achievement of the youth in the fields of science and mathematics.

\end{document}